Supplimentary Analysis

### 2021-11-11 Supplymentary.Rmd
* Successfully Knitting with appendix but formating is not right

```{r EFAResidualsAppB, eval=FALSE, fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE,  results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =35, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

>>>>

```{r EFAResidualsAppB,  fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =35, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
